---
title: "SFThesis"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
maindir <-"C:/Users/Jose/OneDrive/OKCupid"
scriptsdir <-(file.path(maindir,"scripts"))
resultsdir <-(file.path(maindir,"results"))
datadir <- (file.path(maindir,"data"))
#setwd(maindir)
knitr::opts_chunk$set(echo = TRUE)
options(digits = 2)
secondSmall <-read.csv(file.path(datadir,"secondSmall.csv"))
knitr::opts_chunk$set(echo = TRUE)
library(psych)
library(car)
```

#Questions For Thesis
Questions originally selected to be looked at for thesis
```{r Questions for Thesis}
myvars <- c("q12", "q17", "q21","q35", "q36","q106","q122", "q144", "q149", "q152", "q204", "q275", "q294", "q309", "q322", "q323", "q324", "q325", "q326", "q327", "q350", "q352", "q357", "q358", "q360", "q366", "q393", "q444", "q605", "q627", "q1121", "q1128", "q1158", "q1222", "q1447", "q1688", "q4043", "q6413", "q7077", "q7273", "q8054", "q8439", "q12822", "q12832", "q14649", "q14913", "q15565", "q15701", "q15764", "q16371", "q18633", "q18682", "q18691", "q18840", "q18841", "q18902", "q18979", "q18984", "q19236", "q19446", "q19574", "q19832", "q19854", "q19874", "q20021", "q20534", "q22206", "q22991", "q23233", "q24682", "q25294", "q27915", "q28426", "q28820", "q30207", "q33107", "q33593", "q34536", "q35856", "q36045", "q37772", "q38296", "q38646", "q41953", "q42524", "q43261", "q49053", "q54016", "q57717", "q57724", "q59426", "q60500", "q60577", "q61598", "q68307", "q69186", "q69429", "q73389", "q80594", "q81307", "q83114", "q83660", "q83677", "q85272", "q85315", "q85706", "q85999", "q232388", "q19691", "q60394", "q81014", "q1536", "q19691", "q20930", "q401", "q1495", "q15261", "q15778", "q16288","q51155", "q61705", "q67641", "q68235", "q70968", "q47122", "p_trusting", "p_explove",  "q1688","q23618", "q33870", "q37748", "q458", "q56163","q62454", "q47379", "q61666", "q65062", "q1185", "q20135", "q34207", "q35660", "q46091", "q55929", "q20424", "q55587", "q81710", "q83392")

dems <- c("d_relationship", "d_gender", "d_orientation", "d_age", "d_country", "d_ethnicity", "lf_for", "lf_single", "lf_want")

newdata <- secondSmall[myvars]
demographics<- secondSmall[dems]
attach(newdata)

```
#Recodes

use \" for answers with apostrophes or R will not be able to read it
Answers rated in relation to attachment styles/romantic preferences
0=less attachment/interest in long-term monogamy, 1=secure attachment/interest in long-term monogamy

```{r Recodes}

newdata$q12<-recode(q12, "'Yes'=0; 'No' =1")
newdata$q35<-recode(q35, "'Love'=1; 'Sex' =0")
newdata$q17<-recode(q17, "'Yes'=0; 'No' =1")
newdata$q21<-recode(q21, "'Yes'=0; 'No' =1")
newdata$q36<-recode(q36, "'Yes'=0; 'No' =1")
newdata$q106<-recode(q106, "'Yes'=0; 'No' =1")
newdata$q122<-recode(q122, "'A lot'=0; 'A little' =.5; 'Not at all' =1")
newdata$q144<-recode(q144, "'Yes'=0; 'No' =1")
newdata$q149<-recode(q149, "'Passion'=0; 'Dedication' =1")
newdata$q152<-recode(q152, "'Yes'=1; 'No' =0")
newdata$q204<-recode(q204, "'the ability to reproduce'=0; 'the ability to orgasm' =1")
newdata$q275<-recode(q275, "'Yes'=1; 'No' =0")
newdata$q294<-recode(q294, "'Having good sex'=0; 'Having similar political beliefs' =1")
newdata$q309<-recode(q309, "'Yes'=0; 'No' =1")
newdata$q322<-recode(q322, "'Yes'=0; 'No' =1")
newdata$q323<-recode(q323, "'Not really confident'=0; 'Confident' =.5; 'Super confident' =1")
newdata$q324<-recode(q324, "'I agree.' =0; 'I disagree.' =1")
newdata$q325<-recode(q325, "'Yes'=0; 'No' =1")
newdata$q326<-recode(q326, "'Yes'=1; 'No' =0")
newdata$q327<-recode(q327, "'I become less attached.'=0; 'I become more attached.' =0; 'It stays about the same.' =1; \"I told you. I'm a virgin.\" =.5")
newdata$q350<-recode(q350, "'Yes'=1; 'No' =0")
newdata$q352<-recode(q352, "'Extremely hot'=0; 'Extremely honest' =1")
newdata$q357<-recode(q357, "'Drinks and groping'=0; 'Coffee and chit-chat' =1")
newdata$q358<-recode(q358, "'Yes'=1; 'No' =0")
newdata$q393<-recode(q393, "'Yes'=1; 'No' =0")
newdata$q444<-recode(q444, "'Yes'=0; 'No' =1")
newdata$q605<-recode(q605, "'Yes'=1; 'No' =0")
newdata$q627<-recode(q627, "'Yes'=0; 'No' =1")
newdata$q1158<-recode(q1158, "'Yes'=0; 'No' =1")
newdata$q1447<-recode(q1447, "'Yes'=0; 'No' =1; \"I'm Not Sure\" =.5")
newdata$q1688<-recode(q1688, "'Yes'=1; 'No' =0")
newdata$q4043<-recode(q4043, "'Yes'=0; 'No' =1; \"I'm Not Sure\" =.5")
newdata$q6413<-recode(q6413, "'Yes'=0; 'No' =1")
newdata$q7077<-recode(q7077, "'Sex'=0; 'Sleeping' =1")
newdata$q7273<-recode(q7273, "'Yes'=1; 'No' =0; \"I'm a virgin\" = .5")
newdata$q8054<-recode(q8054, "'Yes'=1; 'No' =0")
newdata$q8439<-recode(q8439, "'Take advantage of the situation'=0; 'Absolutely nothing' =1")
newdata$q12822<-recode(q12822, "'Yes'=0; 'No' =1")
newdata$q12832<-recode(q12832, "'Yes'=1; 'No' =0")
newdata$q14649<-recode(q14649, "'Yes'=1; 'No' =0")
newdata$q14913<-recode(q14913, "'Yes'=0; 'No' =1")
newdata$q15701<-recode(q15701, "'Yes'=0; 'No' =1")
newdata$q15764<-recode(q15764, "'Yes'=0; \"I'm Not Sure\" = .5; 'No' =1")
newdata$q16371<-recode(q16371, "'Accept / Are open to non-monogamous relationships.'=0; \"Refuse / Aren't interested in open relationships.\" =1; 'Are hesitant, but would consider it.' =.5")
newdata$q18691<-recode(q18691, "'Yes'=1; \"I'm Not Sure\" = .5; 'No' =0")
newdata$q18902<-recode(q18902, "'Yes' =1; \"I'm Not Sure\" = .5; 'No' =0")
newdata$q19236<-recode(q19236, "'Yes'=0; 'No' =1")
newdata$q19574<-recode(q19574, "'Yes'=0; 'No' =1")
newdata$q19832<-recode(q19832, "'Yes, no matter what.'=1; 'Depends on the circumstances. Distance, time, etc' = .5; \"No, they're not a part of my life anymore.\" =0")
newdata$q19854<-recode(q19854, "'Yes'=0; 'No' =1")
#newdata$q--<-recode(q---, "' Lots of relationships'=0; 'One true love' =1")
newdata$q20021<-recode(q20021, "'Someone for tonight'=0; 'Someone to go out with' = .5; 'Someone to come home to' =1")
newdata$q20534<-recode(q20534, "'Yes' =0; \"I'm Not Sure\" = .5; 'No' =1")
newdata$q22206<-recode(q22206, "'Yes' =0; \"I'm not sure, it depends...\" = .5; 'No way!' =1")
newdata$q22991<-recode(q22991, "'Yes' =1; \"I'm Not Sure\" = .5; 'No' =0")
newdata$q23233<-recode(q23233, "'Yes, absolutely' =1; 'Probably not' = 0; 'No' =0")
newdata$q24682<-recode(q24682, "'True' =0; 'False' =1")
newdata$q25294<-recode(q25294, "'Sure, why not?' =0; 'Depends on the person.' = .5; 'Absolutely NOT.' =1")
newdata$q27915<-recode(q27915, "'Yes' =0; 'Not sure / maybe' = .5; 'No' =1")
newdata$q28426<-recode(q28426, "'Yes' =1; \"I'm Not Sure\" = .5; 'No' =0")
newdata$q33593<-recode(q33593, "'Yes' =0; 'No' =1")
newdata$q34536<-recode(q34536, "'Casual dates, more frequent' =0; 'Serious relationship, less frequent' =1")
newdata$q38296<-recode(q38296, "'Yes.' =0; \"I am already totally 'natural' in this way.\" = .5; 'No.' =1")
newdata$q38646<-recode(q38646, "'Yes.' =0; \"I am already totally 'natural' in this way.\" = .5; 'No.' =1")
newdata$q41953<-recode(q41953, "'One night' =0; 'A few months to a year' = .5; 'Several years' =1; 'The rest of my life' =1")
newdata$q42524<-recode(q42524, "'Yes.' =0; 'No.' =1")
newdata$q54016<-recode(q54016, "'Yes.' =0; 'No.' =1")
newdata$q57717<-recode(q57717, "'Yes.' =1; 'No.' =0")
newdata$q60500<-recode(q60500, "'Yes.' =0; 'No.' =1")
newdata$q60577<-recode(q60577, "'Yes.' =0; 'No.' =1")
newdata$q61598<-recode(q61598, "'Yes.' =0; 'No.' =1")
newdata$q69186<-recode(q69186, "'Yes.' =1; \"I've never had sex with anyone.\" =.5; 'No.' =0")
newdata$q69429<-recode(q69429, "'Yes.' =0; 'No.' =1")
newdata$q73389<-recode(q73389, "'Yes.' =0; 'No.' =1")
newdata$q80594<-recode(q80594, "'Yes.' =1; 'No.' =0")
newdata$q81307<-recode(q81307, "'Yes.' =0; 'No.' =1")
newdata$q83677<-recode(q83677, "'Yes.' =0; 'No.' =1")
newdata$q85272<-recode(q85272, "'I need you.' =0; 'I want you.' =1")
newdata$q85315<-recode(q85315, "'Yes.' =1; \"I haven't had a past relationship.\" =.5; 'No.' =0")
newdata$q85706<-recode(q85706, "'Explore both relationships simultaneously.' =0; 'End the old relationship and pursue the new one.' =0; 'Continue current relationship, ignore attraction.' =1")
newdata$q85999<-recode(q85999, "'Wanting no sex with me at all would be worse.' =0; 'Wanting me only for casual sex would be worse.' =1")
newdata$q232388<-recode(q232388, "\"I'm not friends with any of them.\" =0; \"I'm friends with a few of them.\" =.5; \"I don't have any ex-boyfriends/ex-girlfriends.\" =.5; \"I'm friends with all/most of them.\" =1")
newdata$q19691<-recode(q19691, "'Low' =0; 'Neither high nor low' =.5; 'High' =1")
newdata$q60394<-recode(q60394, "'Yes.' =1; 'It depends upon the situation.' =.5; 'No.' =0")
newdata$q81014<-recode(q81014, "'Yes.' =0; 'It would depend upon the nature of the break up.' =.5; 'No.' =1")
newdata$q1536<-recode(q1536, "'Slow to trust, until worth is proven.' =0; \"I don't know.\" =.5; 'Quick to trust, until proven wrong.' =1")
newdata$q366<-recode(q366, "'Dating multiple people at once' =0; 'Dating one person at a time' =1; \"I only have serious relationships, I don't 'date'\"=1")
newdata$q360<-recode(q360, "'False' =0; 'True' =1")
newdata$q59426<-recode(q59426, "'All of the time.' =0; 'When I was certain the relationship was ending.' =0; 'When the relationship was not going well.' =0; 'After the relationship was formally terminated.' =1")
newdata$q1121<-recode(q1121, "'Yes, and they both knew.' =.5; \"Yes, and I didn't tell at least one of them.\" =0; 'No.' =1")
newdata$q1222<-recode(q1222, "'Someone who turns you on.' =0; 'Someone for whom you would do anything.' =1; \"Someone you feel like you've known forever.\" =1; 'Someone with goals similar to yours.' = 1")
newdata$q18979<-recode(q18979, "'Yes, they have it coming!' =0; \"No, I'd dump them on the spot.\" =.5; \"No, I'd confront them.\" =1; 'Maybe, if one of their friends is cute.' = .5")
newdata$q19446<-recode(q19446, "'Yes, and I still do.' =1; 'No, and I never will.' =1; \"Yes, I have done it, but don't any more.\" =.5; 'No, but I suppose I might.' =.5")
newdata$q1128<-recode(q1128, "'Yes, even in secret.' =0; \"No, it's wrong.\" =1; \"No, but I don't think it's inherently wrong.\" =.5; 'Yes, but only if everybody knew.' =.5")
newdata$q15565<-recode(q15565, "'Yes' =0; 'No' =1")
newdata$q18682<-recode(q18682, "'Yes' =0; 'No' =1")
newdata$q18841<-recode(q18841, "'No.' =0; 'Yes, but only if the sex had been good.' =.5; 'Yes, but only if I liked that person.' =1")
newdata$q18840<-recode(q18840, "'Awful, and I have emotional issues as a result.' =0; 'Wonderful!' =1; \"Not great, but I'm no worse for the wear.\" =.25; 'It was okay.' =.75")
newdata$q18984<-recode(q18984, "'Yes, still waiting on a second chance!' =0; 'Yes, a little.' =.5; 'No, never.' =1")
newdata$q83114<-recode(q83114, "'Yes.' =0; 'No.' =1")
newdata$q83660<-recode(q83660, "'Yes.' =0; 'No.' =1")
newdata$q57724<-recode(q57724, "'Yes.' =0; 'No.' =1")
newdata$q49053<-recode(q49053, "'Less than one year.' =0; 'More than five years.' =1; \"I've never been in a romantic relationship.\" =.5; 'One to five years.' =.5")
newdata$q36045<-recode(q36045, "'No way.' =0; 'Get married yes, settle down no.' =.5; 'Get married no, settle down yes.' =1; 'Absolutely.' =1")
newdata$q37772<-recode(q37772, "'Playing the field' =0; 'Polyamory' =.5; 'An open relationship' =.5; 'Monogamy' =1")
newdata$q19874<-recode(q19874, "'0-6 months' =0; '6-12 months' =.5; \"I've never been in a relationship\" =.5; '12+ months' =1")
newdata$q30207<-recode(q30207, "'Yes, absolutely.' =0; 'Yes, a bit.' =.5; \"No, it's fine.\" =1; \"No, it's underrated.\" =0")
newdata$q33107<-recode(q33107, "'I have open relationships only'= 0; 'Yes, I like that type of polygamy.' =.5; 'I could be convinced by the right people' =.5; 'I am commited to total monogamy' =1")
newdata$q18633<-recode(q18633, "'Yes' =1; \"I'm Not Sure\" = .5; 'I never feel entirely complete' =.5; 'No' =0")
newdata$q28820<-recode(q28820, "'Have great sex' =0; 'Have great ideas' =.5; 'Have great friends' =1; 'Have great love' =1")
newdata$q68307<-recode(q68307, "'Low.' =0; 'Medium.' =.5; 'Zero.' =1; 'High.' =1")
newdata$q43261<-recode(q43261, "'I am my own person.' =0; 'I consider their opinion but go my own way.' =1; 'I always do what my parents say.' =0; 'I almost always do what my parents think is best.' =.5")
newdata$q35856<-recode(q35856, "'Yes.' =1; 'Only if there were good reasons for no contact.' =.5; 'No.' =0")
newdata$q19691.1<-recode(q19691.1, "'Low' =0; 'Neither high nor low' =.5; 'High' =1")
newdata$q20930<-recode(q20930, "'Below average' =0; 'Average' =.5; 'Very, very high' =1; 'Higher than average'=1")


newdata$q47122<-recode(q47122, "'My mother.' =1; 'Someone else.' =0; 'My father.' =1; 'Another relative.' =.5")
newdata$q401<-recode(q401, "'Yes' =1; 'No' =0")
newdata$q1495<-recode(q1495, "'Family' =1; 'Friends' =0")
newdata$q15261<-recode(q15261, "'Yes' =1; 'No' =0")
newdata$q15778<-recode(q15778, "'Yes' =1; 'No' =0; \"I'm Not Sure\" =.5")
newdata$q51155<-recode(q51155, "'Yes.' =1; 'No.' =0; 'Maybe, if they promised to somehow pay me.'=.5")
newdata$q61705<-recode(q61705, "'Yes.' =1; 'No.' =0; 'Maybe.'=.5")
newdata$q68235<-recode(q68235, "'Yes.' =1; 'No.' =0")
newdata$q67641<-recode(q67641, "'Very important.' =1; 'Somewhat important.' =.5; 'Not important.' =0; 'I have no family.' =.5")
newdata$q70968<-recode(q70968, "'Try to reschedule the date.' =1; 'Try to reschedule the funeral.' =.5; 'Go on the date and skip the funeral.' =0; 'Take the date to the funeral.
' =.5")
newdata$q1688.1<-recode(q1688.1, "'Yes' =1; 'No' =0")
#newdata$q23618<-recode(q23618, "'Yes' =1; 'No' =0")
newdata$q33870<-recode(q33870, "'Yes' =1; 'No' =0")
newdata$q37748<-recode(q37748, "'Yes, within reason.' =1; 'No' =0; 'Yes, without question.' =0")
newdata$q458<-recode(q458, "'Yes' =0; 'No' =1")
newdata$q56163<-recode(q56163, "\"I'd be hopeful that they would make the next move.\" =1; \"I'd assume they're busy and leave them alone.\" =1; \"I'd try to contact them repeatedly.\" =0; \"I'd ignore them from now on.\" =0")
newdata$q62454<-recode(q62454, "'Yes' =0; 'No' =1")
newdata$q47379<-recode(q47379, "'Decisions made jointly through consensus.' =1; 'Distribution based upon traditional gender roles.' =.5; 'I would make most of the decisions.' =0; 'My partner would make most of the decisions.' =0")
newdata$q61666<-recode(q61666, "'Not at all important.' =1; 'Somewhat important.' =.5; 'Very important.' =0")
newdata$q65062<-recode(q65062, "'Yes' =0; 'No' =1")
newdata$q1185<-recode(q1185, "'Yes' =1; 'No' =0")
newdata$q20135<-recode(q20135, "'I like to just let it happen' =1; \"I'm indifferent / not sure\" =.5; 'I love it and want it very much' =0; 'I try to avoid it' =0")
newdata$q34207<-recode(q34207, "'Open Book' =1; \"I'm Not Sure\" =.5; 'Secretive' =0; 'Somewhere In Between' =.5")
newdata$q35660<-recode(q35660, "'Always' =1; 'Usually' =1; 'Rarely' =0; 'Never' =0")
newdata$q46091<-recode(q46091, "\"I'd tell them how I feel and we'd go from there.\" =1; \"I'd do nothing and hope it all works itself out.\" =.5; \"I'd break off relations.\" =0; \"I'd use their love for all it's worth.\" =0")
newdata$q55929<-recode(q55929, "'Yes' =0; 'No' =1")
newdata$q20424<-recode(q20424, "'Yes' =0; 'No' =1")
newdata$q55587<-recode(q55587, "'Yes.' =1; 'No.' =0")
newdata$q81710<-recode(q81710, "'Yes.' =1; 'No.' =0")
newdata$q83392<-recode(q83392, "'Yes' =0; 'No' =1")
newdata$q16288<-recode(q16288, "\"Yes, I'd be dating them not their family.\" =0; 'No, What the heck are they hiding?' =1; 'Dunno, depends.'=.5")

w <- which( sapply( newdata, 
                    class ) == 'factor' )

newdata[w] <- lapply( newdata[w], 
                   function(x)
                     as.numeric(as.character(x)) )

#Reverse code certain questions (anxious and avoidant attachment scales)
columnsToReverse <- c("q1185", "q15701", "q19236", "q20135", 
"q34207", 
"q35660", "q4043", 
"q444", 
"q46091", 
"q55929", 
"q57724", "q85706", 
"q20424",
"q83392","q15764", 
"q1688", 
"q18633", 
"q18984", 
"q23618", 
"q33870", 
"q37748", 
"q458", 
"q56163", 
"q61598", 
"q62454", 
"q85272", 
"q47379", 
"q61666", "q69429", 
"q59426", "q24682"
,"q83114")
newdata[,columnsToReverse] = lapply(columnsToReverse,  function(x) 1 - newdata[, x])
```

"We used an iterative approach to scale analysis to (a) estimate interitem reliability... (b) drop items which did not contribute to alpha... etc. (c) we weren't a slave to this (d) we reexamined scale meaning after this process was complete. See https://www.personality-project.org/r/html/score.items.html" - Lanning

#Alpha Level for Relationship Questions

##Alpha for Monogamy Preference
```{r Alpha for Monogamy Preference}
myKeys<-list(mono=c("q106", "q1128", "q1158","q23233", "q85315", "q41953", "q8054", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294"))
mono<-scoreItems(myKeys,newdata)
lengths(mono)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.68
```

```{r}
myKeys<-list(mono=c("q106", "q1128", "q1158","q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294"))  #"q8054", 
mono<-scoreItems(myKeys,newdata)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.7
```

```{r}
myKeys<-list(mono=c("q106", "q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294"))#"q8054","q1158"
mono<-scoreItems(myKeys,newdata)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.7
```

```{r}
myKeys<-list(mono=c("q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294")) #"q1158","q106","q8054", 
mono<-scoreItems(myKeys,newdata)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.71
```
The alpha for the mono scale was `r mono["alpha"]`.
```{r}
myKeys<-list(mono=c( "q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q25294")) # "q393", "q106", "q1158", "q8054",
mono<-scoreItems(myKeys,newdata)
mono["alpha"]
mono["item.cor"]
MonoScores<-mono["scores"]
lengths(mono)
#alpha=0.75
#alpha does not exceed 0.75
monogamyScores <- mono[["scores"]]
```
##Alpha for Relationship Length
```{r Alpha for Relationship Length}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q49053", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q323", "q324", "q358", "q444", "q627", "q1447", "q6413", "q7077", "q7273", "q8439", "q14913", "q15701", "q18841", "q19446", "q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q294", "q352", "q357", "q19874", "q20021"))
long<-scoreItems(myKeys,newdata)
lengths(long)
#long["alpha"]
#long["item.cor"]
#alpha=0.75
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q49053", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q358", "q444", "q627", "q1447", "q6413", "q7077", "q7273", "q8439", "q14913", "q15701", "q18841", "q19446","q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q294", "q352", "q357", "q19874", "q20021"))#"q323",
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.76
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q49053", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q358", "q444", "q627", "q1447", "q6413", "q7077", "q7273", "q8439", "q14913", "q15701", "q18841", "q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q294", "q352", "q357", "q19874", "q20021"))# "q323","q19446",
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.76
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q49053", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q358", "q444", "q627", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841", "q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q294", "q352", "q357", "q19874", "q20021")) #"q19446","q7273","q323"
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.78
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q358", "q444", "q627", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841", "q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q352", "q357", "q19874", "q20021")) #"q19446","q7273","q323","q294"
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.79
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q444", "q627", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841", "q42524","q69186", "q81307", "q83677", "q35", "q149", "q352", "q357", "q19874", "q20021")) #"q19446","q7273","q323","q294","q204"
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.81
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q444", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841", "q42524", "q69186", "q81307", "q83677", "q35", "q149", "q352", "q357", "q19874", "q20021")) #"q19446","q7273","q323","q294","q204","q627","q358","q57717","q49053","q34536"
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.82
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q444", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841", "q69186", "q81307", "q83677", "q35", "q149", "q352", "q357", "q19874", "q20021")) #"q19446","q7273","q323","q294","q204","q627","q358","q57717","q49053","q34536", "q42524"
long<-scoreItems(myKeys,newdata)
#long["alpha"]
#long["item.cor"]
#alpha=0.83
```
The alpha for the long scale was `r long["alpha"]`.
```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q444", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841", "q69186", "q81307", "q83677", "q35", "q352", "q357", "q19874", "q20021")) #"q19446","q7273","q323","q294","q204","q627","q358","q57717","q49053","q34536", "q42524","q149"
long<-scoreItems(myKeys,newdata)
long["alpha"]
long["item.cor"]
lengths(long)
#alpha=0.84
#alpha does not go higher than 0.84
```
##Alpha For Remaining Relationship Questions
```{r Alpha for remaining relationship questions}
#all remaining relationship questions that were not commented out
#data(newdata)
myKeys<-list(relationships=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841","q69186", "q81307", "q83677", "q35","q352", "q357", "q19874", "q20021","q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q25294"))
relationships<-scoreItems(myKeys,newdata)
relationships["alpha"]
relationships["item.cor"]
#alpha when runnning the remaining set of questions from the relationship set in total is 0.88
#alpha does not exceed 0.88
```

I realized I forgot to include "p_explove" when working with Tiny
When I included it, alpha dropped from .89 to 0.07 in Tiny
Personality variables will be excluded from these calculations of alpha due to their massive effect on (decreasing) alpha, as was also seen in Karly's dataset


#Alpha Level for Attachment Questions

The attachment questions will feature three scales: a family/childhood scale (which will ask about parents, childhood expreiences, and feelings toward family), an anxious attachment sclae (measure anxious attachment style), and an avoidant attachment scale (measure avoidant attachment style). Four types of attachment styles will be assessed in the users. Securely attached individuals will have low scores in the anxious and avoidant scales and a high score on the childhood scale. Anxiously attached individuals will score high in the anxious scale and low in the avoidant and childhood scales. Avoidantly attached individuals will score high in the avoidant scale and low  in the anxious and family scales. Fearful (anxious-avoidant) attachment will have high scores on both the anxious and avoidant scales and a low score on the family/childhood scale.

##Alpha for Childhood and Family Relations
```{r}
myKeys<-list(family=c("q350", "q401", "q1495", "q15261", "q15778", "q16288", "q18840", "q19832", "q22991", "q43261", "q51155", "q61705", "q67641", "q68235", "q70968", "q47122"))
family<-scoreItems(myKeys,newdata)
#family["alpha"]
#family["item.cor"]

#alpha=0.57
#q15778, q16288, q51155, q61705, q68235 had no variance and were deleted 
```

```{r}
myKeys<-list(family=c("q350", "q401", "q1495", "q15778", "q16288", "q18840", "q19832", "q43261", "q51155", "q67641", "q68235", "q70968", "q47122")) #"q61705","q15261","q22991"
family<-scoreItems(myKeys,newdata)
family["alpha"]
family["item.cor"]

#alpha=0.6
```
##Alpha for Anxious Attachment Style
```{r}
myKeys<-list(anx=c("q15764", "q1688", "q18633", "q18984", "q33870", "q37748", "q458", "q56163", "q61598", "q62454", "q85272", "q47379", "q59426", "q20424", "q24682"))#"q61666", "q69429", "q83114"

anx<-scoreItems(myKeys,newdata)
anx["alpha"]
anx["item.cor"]
lengths(anx)

#q62454 had no variance and was deleted
#alpha=.58
```
The alpha for the anx scale was `r anx["alpha"]`.

##Alpha for Avoidant Attachment Style
```{r}
myKeys<-list(avoid=c("q1185", "q15701", "q19236", "q20135", "q35660", "q4043", "q444", "q46091", "q57724", "q85706", "q20424","q24682")) #"q83114","q83392","q55929","q34207"
avoid<-scoreItems(myKeys,newdata)
avoid["alpha"]
avoid["item.cor"]

#q55929 and q83392 had no variance and were deleted
#alpha=.42
```
The alpha for the avoidant scale was `r avoid["alpha"]`.

#Scale Scores
```{r Scores}
monogamyScores <- mono[["scores"]]
lengthScores <- long[["scores"]]
relationshipScores <- relationships[["scores"]]
childhoodScores <- family[["scores"]]
anxiousScores <- anx[["scores"]]
avoidantScores <- avoid[["scores"]]
SFscaleScores <-cbind(monogamyScores,
                      lengthScores,
                      relationshipScores,
                      childhoodScores,
                      anxiousScores,
                      avoidantScores)
```
#Attachment Style Classification
```{r Attachment Style Classification}
#median(childhoodScores)=.86

#A basic way of looking at attachment from three classifications:
#AttachmentCategory <- ifelse(childhoodScores > .85, print("secure"), ifelse(anxiousScores > avoidantScores, print("anxious"), print("avoidant")))

#If I want to include a fearful attachment style, I should use something like this:
AttachmentCategory <- ifelse (childhoodScores > .85, 
                                  print("secure"), 
                      ifelse
                           ((anxiousScores < 1.2*avoidantScores & 
                               anxiousScores > .8*avoidantScores) &
                           (avoidantScores < 1.2*anxiousScores & 
                               avoidantScores > .8*anxiousScores), 
                                  print("fearful"), 
                      ifelse
                           (avoidantScores > anxiousScores, 
                                  print("avoidant"), 
                                  print("anxious")
                             )))
#Secure attacchments are usually 50-70% of population, depending on study
#prevelance of each type of insecure attachment varies depending on study and number of insecure attachments identified
#Generally, more people have an avoidant attachment style than anxious, and more people have an anxious attachment style than a fearful attachment style
#The difference between each insecure attachment style prevalence varies based on the study

colnames(AttachmentCategory)[colnames(AttachmentCategory)=="family"] <- "AttachmnetStyle"
colnames(AttachmentCategory)

sum(AttachmentCategory=="secure")
sum(AttachmentCategory=="avoidant")
sum(AttachmentCategory=="anxious")
sum(AttachmentCategory=="fearful")
```
Using this function on the data, approxiamately 65.6% of people are securely attached, 14% are avoidantly attached, 15.4% are anxiously attached, and 5% are fearfully attached, which is similar to what other researchers have found.


#Means of Scale Scores
```{r}
library(tibble)
library(magrittr)
library(dplyr)
SFscaleScores %>% 
  as.tibble() %>% 
  summarise_all(funs(mean))

#write.csv(SFscaleScores,"SFscaleScores.csv",
 #         row.names = FALSE)
```


```{r Data Table}
library(papeR)
library(knitr)

kable(summarize(newdata, type = "numeric"))
```
#Demographics
Below is demographic information about users and certain preferences they are looking for in their potential matches
The average age of individuals in the sample is `r (round(mean(newdata$d_age, na.rm=TRUE),2))`.
```{r Demographics}
mean(d_age, na.rm=TRUE)
min(d_age, na.rm = TRUE)
max(d_age, na.rm = TRUE)

sum(d_gender=="Man", na.rm=TRUE)
sum(d_gender=="Woman", na.rm=TRUE)
sum(d_relationship=="Single", na.rm=TRUE)
sum(d_relationship=="Seeing Someone", na.rm=TRUE)
sum(d_relationship=="Married", na.rm=TRUE)
sum(d_relationship=="Open relationship", na.rm=TRUE)

sum(lf_single=="Who are single", na.rm=TRUE)
sum(grepl("long-term dating", lf_for))
sum(grepl("short-term dating", lf_for))
sum(grepl("casual sex", lf_for))
sum(grepl("For  new friends", lf_for))
```

```{r}
demographicScales <- cbind(demographics, AttachmentCategory, SFscaleScores)
#write.csv(demographicScales,"soniaDemScales.csv", row.names = FALSE)
```
