---
title: "SFThesis"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(psych)
#library(car)
#install.packages("lubridate")
library(lubridate)
library(tidyverse)
library(knitr)
maindir <- "C:/Users/Jose/OneDrive/OKCupid"
#maindir <- getwd()
scriptsdir <- (file.path(maindir,"scripts"))
resultsdir <- (file.path(maindir,"results"))
datadir <- (file.path(maindir,"data"))
#setwd(maindir)
knitr::opts_chunk$set(echo = TRUE)
options(digits = 2)
newdata <- read_csv("bigsoniaRecodes.csv")
demographics <- read_csv("bigdemographicdata.csv")

```

#Alpha Level for Relationship Questions

##Alpha for Monogamy Preference
delete=FALSE needs to be set or all items are deleted for lack of variance
```{r Alpha for Monogamy Preference, include=FALSE}
myKeys<-list(mono=c("q106", "q1128", "q1158","q23233", "q85315", "q41953", "q8054", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294"))
mono<-scoreItems(myKeys,newdata, delete = FALSE)
lengths(mono)
mono["alpha"]
mono["item.cor"]
#alpha=0.7
```

```{r, include=FALSE}
myKeys<-list(mono=c("q106", "q1128", "q1158","q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294"))  #"q8054", 
mono<-scoreItems(myKeys,newdata, delete=FALSE)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.7
```

```{r, include=FALSE}
myKeys<-list(mono=c("q106", "q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294"))#"q8054","q1158"
mono<-scoreItems(myKeys,newdata, delete=FALSE)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.7
```

```{r, include=FALSE}
myKeys<-list(mono=c("q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q393", "q25294")) #"q1158","q106","q8054", 
mono<-scoreItems(myKeys,newdata, delete = FALSE)
#mono["alpha"]
#mono["item.cor"]
#alpha=0.72

```

```{r}
myKeys<-list(mono=c( "q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q25294")) # "q393", "q106", "q1158", "q8054",
mono<-scoreItems(myKeys,newdata, delete = FALSE)
mono["alpha"]
mono["item.cor"]
MonoScores<-mono["scores"]
lengths(mono)
#alpha=0.76
#alpha does not exceed 0.76
monogamyScores <- mono[["scores"]]
```
The alpha for the monogamy scale was `r mono["alpha"]`.

##Alpha for Relationship Length
```{r Alpha for Relationship Length, include=FALSE}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045", "q49053", "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q323", "q324", "q358", "q444", "q627", "q1447", "q6413", "q7077", "q7273", "q8439", "q14913", "q15701", "q18841", "q19446", "q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q294", "q352", "q357", "q19874", "q20021"))
long<-scoreItems(myKeys,newdata, delete=FALSE)
lengths(long)
long["alpha"]
long["item.cor"]
alpha=0.68
```

```{r, include=FALSE}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045",  "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q358", "q627", "q1447", "q6413", "q7077", "q8439", "q14913", "q18841", "q19446","q42524", "q69186", "q81307", "q83677", "q35", "q149", "q204", "q294", "q352", "q357", "q19874", "q20021"))#"q49053","q444", "q7273", "q323","q15701"
long<-scoreItems(myKeys,newdata, delete=FALSE)
long["alpha"]
long["item.cor"]
#alpha=0.71
```

```{r, include=FALSE}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045",  "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q358", "q627", "q1447", "q6413", "q7077", "q8439", "q14913", "q18841","q42524", "q69186", "q81307", "q83677", "q35", "q149", "q352", "q357", "q19874", "q20021"))#"q49053","q444", "q7273", "q323","q15701", "q19446", "q294", "q204"
long<-scoreItems(myKeys,newdata, delete=FALSE)
long["alpha"]
long["item.cor"]
#alpha=0.72
```

```{r, include=FALSE}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q34536", "q36045",  "q57717", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q627", "q1447", "q6413", "q7077", "q8439", "q14913", "q18841","q42524", "q69186", "q81307", "q83677", "q35", "q149", "q352", "q357", "q19874", "q20021"))#"q49053","q444", "q7273", "q323","q15701", "q19446", "q294", "q204", "q358"
long<-scoreItems(myKeys,newdata, delete=FALSE)
long["alpha"]
long["item.cor"]
#alpha=0.73
```

```{r, include=FALSE}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q1447", "q6413", "q7077", "q8439", "q14913", "q18841","q42524", "q69186", "q81307", "q83677", "q35", "q149", "q352", "q357", "q19874", "q20021"))#"q49053","q444", "q7273", "q323","q15701", "q19446", "q294", "q204", "q358", "q34536", "q627",  "q57717"
long<-scoreItems(myKeys,newdata, delete=FALSE)
long["alpha"]
long["item.cor"]
#alpha=0.73
```

```{r}
myKeys<-list(long=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q1447", "q6413", "q7077", "q8439", "q14913", "q18841", "q69186", "q81307", "q83677", "q35", "q352", "q357", "q19874", "q20021"))#"q49053","q444", "q7273", "q323","q15701", "q19446", "q294", "q204", "q358", "q34536", "q627",  "q57717","q42524", "q149"
long<-scoreItems(myKeys,newdata, delete = FALSE)
long["alpha"]
long["item.cor"]
#alpha=0.75
#alpha does not go higher than 0.75
```
The alpha for the long scale was `r long["alpha"]`.

##Alpha For Remaining Relationship Questions
```{r Alpha for remaining relationship questions}
#all remaining relationship questions that were not commented out
#data(newdata)
myKeys<-list(relationships=c("q326", "q360", "q1222", "q18691", "q36045", "q12", "q17", "q21", "q122", "q144", "q152", "q309", "q322", "q324", "q1447", "q6413", "q7077", "q8439", "q14913", "q15701", "q18841","q69186", "q81307", "q83677", "q35","q352", "q357", "q19874", "q20021","q1128", "q23233", "q85315", "q41953", "q37772", "q36", "q325", "q366", "q1121", "q16371", "q18902", "q33107", "q25294"))
relationships<-scoreItems(myKeys,newdata, delete=FALSE)
relationships["alpha"]
relationships["item.cor"]
#alpha when runnning the remaining set of questions from the relationship set in total is 0.83
#alpha does not exceed 0.83

```
I realized I forgot to include "p_explove" when working with Tiny
When I included it, alpha dropped from .89 to 0.07 in Tiny
Personality variables will be excluded from these calculations of alpha due to their massive effect on (decreasing) alpha, as was also seen in Karly's dataset


#Alpha Level for Attachment Questions

The attachment questions will feature three scales: a family/childhood scale (which will ask about parents, childhood expreiences, and feelings toward family), an anxious attachment sclae (measure anxious attachment style), and an avoidant attachment scale (measure avoidant attachment style). Four types of attachment styles will be assessed in the users. Securely attached individuals will have low scores in the anxious and avoidant scales and a high score on the childhood scale. Anxiously attached individuals will score high in the anxious scale and low in the avoidant and childhood scales. Avoidantly attached individuals will score high in the avoidant scale and low  in the anxious and family scales. Fearful (anxious-avoidant) attachment will have high scores on both the anxious and avoidant scales and a low score on the family/childhood scale.

##Alpha for Childhood and Family Relations
```{r, include=FALSE}
myKeys<-list(family=c("q350", "q401", "q1495", "q15261", "q15778", "q16288", "q18840", "q19832", "q22991", "q43261", "q51155", "q61705", "q67641", "q68235", "q70968", "q47122"))
family<-scoreItems(myKeys,newdata, delete = FALSE)
family["alpha"]
family["item.cor"]

#alpha=0.49
#47122 had no variance and was deleted 
```

```{r}
myKeys<-list(family=c("q350", "q401", "q1495", "q15778", "q16288", "q18840", "q19832", "q43261", "q51155", "q67641", "q68235", "q70968", "q47122")) #"q61705","q15261","q22991"
family<-scoreItems(myKeys,newdata, delete = FALSE)
family["alpha"]
family["item.cor"]

#alpha=0.53
```
##Alpha for Anxious Attachment Style
```{r}
myKeys<-list(anx=c("q15764", "q1688", "q18633", "q18984", "q33870", "q37748", "q458", "q56163", "q61598", "q62454", "q85272", "q47379", "q59426", "q20424", "q24682"))#"q61666", "q69429", "q83114"

anx<-scoreItems(myKeys,newdata, delete = FALSE)
anx["alpha"]
anx["item.cor"]
lengths(anx)

#alpha=.6
```
The alpha for the anx scale was `r anx["alpha"]`.

##Alpha for Avoidant Attachment Style
```{r}
myKeys<-list(avoid=c(
  #"q1185", 
  "q15701", "q19236", "q20135", "q35660", "q4043", "q444", "q46091", "q57724", "q85706", "q20424","q24682", #"q83114",
                     "q83392" #,"q55929"
                     #,"q34207"
                     )) 
avoid<-scoreItems(myKeys, newdata, delete = FALSE)
avoid["alpha"]
avoid["item.cor"]

#q55929 had no variance and was deleted
#alpha=.44
```
#Scale Scores
```{r}
monogamyScores <- mono[["scores"]]
lengthScores <- long[["scores"]]
relationshipScores <- relationships[["scores"]]
childhoodScores <- family[["scores"]]
anxiousScores <- anx[["scores"]]
avoidantScores <- avoid[["scores"]]
SFscaleScores <-cbind(monogamyScores,
                      lengthScores,
                      relationshipScores,
                      childhoodScores,
                      anxiousScores,
                      avoidantScores)
```

```{r}
#Monogamy Scores 
  min(monogamyScores)
  max(monogamyScores)
  median(monogamyScores)
  mean(monogamyScores)
  sd(monogamyScores)
#Length Scores
  min(lengthScores)
  max(lengthScores)
  median(lengthScores)
  mean(lengthScores)
  sd(lengthScores)
cor(monogamyScores, lengthScores)
#Attachment Scores
min(childhoodScores)
  max(childhoodScores)
  mean(childhoodScores)
  sd(childhoodScores)
min(avoidantScores)
  max(avoidantScores)
  mean(avoidantScores)
  sd(avoidantScores)
min(anxiousScores)
  max(anxiousScores)
  mean(anxiousScores)
  sd(anxiousScores)

```
#Attachment Style Classification
```{r Attachment Style Classification}
#median(childhoodScores)=.86 for 2000sample

#A basic way of looking at attachment from three classifications:
#AttachmentCategory <- ifelse(childhoodScores > .86, print("secure"), ifelse(anxiousScores > avoidantScores, print("anxious"), print("avoidant")))

#If I want to include a fearful attachment style, I should use something like this:
AttachmentCategory <- ifelse (childhoodScores > .86, 
                                  print("secure"), 
                      ifelse
                           ((anxiousScores < 1.2*avoidantScores & 
                               anxiousScores > .8*avoidantScores) &
                           (avoidantScores < 1.2*anxiousScores & 
                               avoidantScores > .8*anxiousScores), 
                                  print("fearful"), 
                      ifelse
                           (avoidantScores > anxiousScores, 
                                  print("avoidant"), 
                                  print("anxious")
                             )))

#Secure attacchments are usually 50-70% of population, depending on study
#prevelance of each type of insecure attachment varies depending on study and number of insecure attachments identified
#Generally, more people have an avoidant attachment style than anxious, and more people have an anxious attachment style than a fearful attachment style
#The difference between each insecure attachment style prevalence varies based on the study
colnames(AttachmentCategory)[colnames(AttachmentCategory)=="family"] <- "AttachmentStyle" #rename column

#Calulate percentage of each attachment style
(sum(AttachmentCategory=="secure"))/66271 #percent securely attached
(sum(AttachmentCategory=="avoidant"))/66271 #percent avoidantly attached
(sum(AttachmentCategory=="anxious"))/66271 #percent anxiously attached
(sum(AttachmentCategory=="fearful"))/66271 #percent fearfully attached

```
Using this function on the data, approxiamately 63.3% of people are securely attached, 18% are avoidantly attached, 17.2% are anxiously attached, and 1.5% are fearfully attached, which is similar to what other researchers have found.

#Means of Scale Scores
```{r}
SFscaleScores %>% 
  as.tibble() %>%
  summarise_all(funs(mean))

write.csv(SFscaleScores,"SFscaleScores.csv",
          row.names = FALSE)
```

#Demographihcs
Below is demographic information about users and certain preferences they are looking for in their potential matches.
The average age of individuals in the sample is `r (round(mean(newdata$d_age, na.rm=TRUE),2))`.
```{r Demographics}
attach(demographics)
mean(d_age, na.rm=TRUE)
min(d_age, na.rm = TRUE)
max(d_age, na.rm = TRUE)
sd(d_age, na.rm=TRUE)

sum(d_gender=="Man", na.rm=TRUE)
sum(d_gender=="Woman", na.rm=TRUE)
sum(d_relationship=="Single", na.rm=TRUE)
sum(d_relationship=="Seeing Someone", na.rm=TRUE)
sum(d_relationship=="Married", na.rm=TRUE)
sum(d_relationship=="Open relationship", na.rm=TRUE)

sum(lf_single=="Who are single", na.rm=TRUE)
sum(grepl("long-term dating", lf_for))
sum(grepl("short-term dating", lf_for))
sum(grepl("casual sex", lf_for))
sum(grepl("For  new friends", lf_for))
```

```{r, include=FALSE}
demographicScales <- cbind(demographics, SFscaleScores, AttachmentCategory)
write.csv(demographicScales,"bigsoniaDemScales.csv", row.names = FALSE)
```

```{r, include=FALSE}
demographicScales<- demographicScales[,-16]
```
